---
title: "Assignment 1"
---

This repository contains my submission for Assignment 1.

1.  **Anscombe’s quartet**

```{r}
options(repos = c(CRAN = "https://cran.rstudio.com/"))
data(anscombe)  # Load Anscombe's data
View(anscombe) # View the data
summary(anscombe)

## Simple version
plot(anscombe$x1,anscombe$y1)
summary(anscombe)

# Create four model objects
lm1 <- lm(y1 ~ x1, data=anscombe)
summary(lm1)
lm2 <- lm(y2 ~ x2, data=anscombe)
summary(lm2)
lm3 <- lm(y3 ~ x3, data=anscombe)
summary(lm3)
lm4 <- lm(y4 ~ x4, data=anscombe)
summary(lm4)
plot(anscombe$x1,anscombe$y1)
abline(coefficients(lm1))
plot(anscombe$x2,anscombe$y2)
abline(coefficients(lm2))
plot(anscombe$x3,anscombe$y3)
abline(coefficients(lm3))
plot(anscombe$x4,anscombe$y4)
abline(coefficients(lm4))
```

2.  **Generative Art (Fall Color)**

```{r}
install.packages("ggplot2")
library(ggplot2)
n <- 100
angles <- seq(0, 2*pi, length.out = n)
x <- cos(angles)
y <- sin(angles)
df <- data.frame(
  x = x * seq(0.1, 1, length.out = n),
  y = y * seq(0.1, 1, length.out = n),
  size = seq(1, 10, length.out = n)
)
ggplot(df, aes(x = x, y = y)) +
  geom_point(aes(size = size), shape = 21, fill = "lightblue", color = "black", alpha = 0.6) +
  theme_void() + 
  coord_fixed()

```

3.  **Run Fall.R**

```{r}
# Install packages
install.packages(c("gsubfn", "proto", "tidyverse"))

library(gsubfn)
library(tidyverse)

# Define elements in plant art
# Each image corresponds to a different axiom, rules, angle and depth

# Leaf of Winter (Modified)
axiom="X"
rules=list("X"="F-[[X]+X]+F[+FX]-X", "F"="FF")
angle=22.5
depth=6

for (i in 1:depth) axiom=gsubfn(".", rules, axiom)

actions=str_extract_all(axiom, "\\d*\\+|\\d*\\-|F|L|R|\\[|\\]|\\|") %>% unlist

status=data.frame(x=numeric(0), y=numeric(0), alfa=numeric(0))
points=data.frame(x1 = 0, y1 = 0, x2 = NA, y2 = NA, alfa=90, depth=1)

# Generating data
for (action in actions)
{
  if (action=="F")
  {
    x=points[1, "x1"]+cos(points[1, "alfa"]*(pi/180))
    y=points[1, "y1"]+sin(points[1, "alfa"]*(pi/180))
    points[1,"x2"]=x
    points[1,"y2"]=y
    data.frame(x1 = x, y1 = y, x2 = NA, y2 = NA,
               alfa=points[1, "alfa"],
               depth=points[1,"depth"]) %>% rbind(points)->points
  }
  if (action %in% c("+", "-")){
    alfa=points[1, "alfa"]
    points[1, "alfa"]=eval(parse(text=paste0("alfa",action, angle)))
  }
  if(action=="["){
    data.frame(x=points[1, "x1"], y=points[1, "y1"], alfa=points[1, "alfa"]) %>%
      rbind(status) -> status
    points[1, "depth"]=points[1, "depth"]+1
  }

  if(action=="]"){
    depth=points[1, "depth"]
    points[-1,]->points
    data.frame(x1=status[1, "x"], y1=status[1, "y"], x2=NA, y2=NA,
               alfa=status[1, "alfa"],
               depth=depth-1) %>%
      rbind(points) -> points
    status[-1,]->status
  }
}

# Plot with Winter Color Palette
ggplot() +
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2),
               lineend = "round",
               color="lightblue", # Winter color theme (modified)
               data=na.omit(points)) +
  coord_fixed(ratio = 1) +
  theme_void() # No grid nor axes
```

4.  **Chart Critique**

Chart Critique: "U.S. Unemployment Rate by Race" from the New York Times Source: New York Times Chart Type: Line Chart

Strengths: Clear Trend Representation: Effectively shows changes in unemployment rates over time for different racial groups. Distinct Colors: Colors clearly differentiate the racial groups. Appropriate Time-Series Chart: Suitable for visualizing unemployment trends over several years. Areas for Improvement: Overlapping Lines: Similar unemployment rates across groups cause overlap, making it hard to distinguish lines. Lack of Data Markers: Adding markers at key points (e.g., during the COVID-19 spike) would enhance readability. Legend Placement: The distant legend forces viewers to switch focus between the chart and legend. Axes Labels: More granular y-axis labels (e.g., showing increments of 0.5%) would improve precision. Suggested Improvements: Add data markers and reduce line overlap with transparency or alternative line styles. Move the legend closer to the chart or label lines directly for easier interpretation. Include more precise axis labels for clearer comparisons.
